The finite base property for some relation algebras subreducts

### 2020-07-03 problem-19.17/Text.tex
R(;, \vee)-update

Let $A$ be a set of binary relations on some base set $W$ such that $R = \cup A$ is transitive and $\{ x, y \: | \: x R y \} = W$ as in Definition~\ref{rrs}. A relation join-semilattice ordered semigroup (${\bf ROS^{\vee}}$) is an algebra of binary relations $\mathcal{A} = \langle A, |, \cup \rangle$ such that $;$ is a relation composition as above and $\cup$ is the set-theoretic union. Let us define a representation of
\begin{defin}
  Let $\mathcal{S} = \langle S, \cdot, \vee \rangle$ a join-semilattice ordered semigroup. A representation of $\mathcal{S}$ is a map
  $h : S \to 2^{D \times D}$ for some base set $D$ satisfying the following conditions
  \begin{itemize}
    \item $h(a) = h(b) \Rightarrow a = b$
    \item $h(a \vee b) = h(a) \vee h(b)$
    \item $h(a ; b) = h(a) | h(b) = \{ (e,d) \in D \times D \: | \: \exists f \in D \: (e,f) \in h(a) \: \& \: (f,d) \in h(b) \}$
  \end{itemize}
\end{defin}
It is known that the class of all representable join-semilattice ordered semigroups has no finite axiomatisation \cite{andreka1989union}. In other words,

@@

\begin{lemma}
  For each $n < \omega$, $\mathfrak{A}_n$ does not belong ${\bf RRA}$. The $(\vee, ;)$-reduct $\mathfrak{S}_n$ of $\mathfrak{A}_n$ is not representable as well.
\end{lemma}

@@

  We prove that  
\end{proof}

>>>>

Let $A$ be a set of binary relations on some base set $W$ such that $R = \cup A$ is transitive and $\{ x, y \: | \: x R y \} = W$ as in Definition~\ref{rrs}. A relation join-semilattice ordered semigroup (${\bf ROS^{\vee}}$) is an algebra of binary relations $\mathcal{A} = \langle A, |, \cup \rangle$ such that $;$ is a relation composition as above and $\cup$ is the set-theoretic union.

Recall that a class of structures ${\bf K}$ is called finitely axiomatisable iff both ${\bf K}$ and its complement are closed
ultraproducts and isomorphic copies.

It is known that the class of all representable join-semilattice ordered semigroups has no finite axiomatisation \cite{andreka1989union}. In other words,

@@

\begin{lemma}
  For each $n < \omega$, $\mathfrak{A}_n$ does not belong ${\bf RRA}$. The $(\vee, ;)$-reduct $\mathfrak{S}_n$ of $\mathfrak{A}_n$ is not representable as well. For each $n < \omega$, there is an equation valid in set algebras failing in $\mathfrak{S}_n$.
\end{lemma}

@@

  We prove that $\mathfrak{S}_n$ is not representable by contradiction.
  Suppose $h$ is an isomorphism of $\mathfrak{S}_n$ to a set relation of relations having similarity type $\{ ;, \vee \}$. Let $0$ be a zero element of $\mathfrak{A}_n$.
\end{proof}

TODO: define games and networks. Take a look at \cite{hirsch1997step}.

\begin{lemma}
  Any non-trivial ultraproduct of $\{ \mathfrak{A}_n \}_{n < \omega}$ is representable.
\end{lemma}

\begin{lemma}
  TODO: one needs to realise when $\exists$ has a winning strategy
\end{lemma}
